A parametric system for adaptive extrusion width contour parallel toolpath generation

### 2019-08-16 4_method.tex
overview figure

\begin{enumerate}
\item Compute a skeleton of the outline shape.
\item Use a significance measure to mark regions of the skeleton which are central.
\item Determine the bead count values in the marked regions and handle transitions to different bead count values.
\item Generate junctions along unmarked bones of the skeleton and connect the junctions together to form the extrusion beads.
\end{enumerate}

@@

>>>>

\begin{enumerate}
\item Compute a skeleton of the outline shape.
\item Use a significance measure to mark regions of the skeleton which are central.
\item Determine the bead count values in the marked regions and handle transitions to different bead count values.
\item Generate junctions along unmarked bones of the skeleton and connect the junctions together to form the extrusion beads.
\end{enumerate}
See \cref{overview_fig}.

@@

\begin{figure*}
\centering
\setlength{\figwidth}{0.19\textwidth}
\begin{subfigure}{\figwidth}
\centering
\includegraphics[width=\columnwidth]{sources/method/overview/skeleton.pdf}
\caption{Skeleton}\label{overview_fig_skeleton}
\end{subfigure}
\begin{subfigure}{\figwidth}
\centering
\includegraphics[width=\columnwidth]{sources/method/overview/marked.pdf}
\caption{Marked}\label{overview_fig_marked}
\end{subfigure}
\begin{subfigure}{\figwidth}
\centering
\includegraphics[width=\columnwidth]{sources/method/overview/transitions.pdf}
\caption{Transitions}\label{overview_fig_transitions}
\end{subfigure}
\begin{subfigure}{\figwidth}
\centering
\includegraphics[width=\columnwidth]{sources/method/overview/junctions.png}
\caption{Junctions}\label{overview_fig_junctions}
\end{subfigure}
\begin{subfigure}{\figwidth}
\centering
\includegraphics[width=\columnwidth]{sources/method/overview/toolpaths.png}
\caption{Toolpaths}\label{overview_fig_toolpaths}
\end{subfigure}
\caption{
Overview of the steps in the method of our framework.
First we \subref{overview_fig_skeleton} decompose the outline shape into a skeleton (grey), \subref{overview_fig_marked} mark central regions (blue) and determine an initial bead count (numbers) based on the local feature size.
Then we \subref{overview_fig_transitions} make alterations to smoothly transition to a different bead count (magenta).
We then \subref{overview_fig_junctions} generate a number of junctions (yellow) equal to the bead count along the bones of the skeleton,
which are \subref{overview_fig_toolpaths} connected together to make the toolpaths.
}
\label{overview_fig}
\end{figure*}
